Succinct representations for abstract interpretation

### 2011-10-28 papers/PLDI2012/implicitization.tex
conclusion bof

>>>>

We focused on numerical properties, because they are supported by easily available abstract libraries. Yet, in most programs, properties of data structures are important for proving interesting properties. Further investigations are needed not only on good abstractions for pointers (many are already known) but also on their conversion to SMT problems.
